---
title: "MODULES 07 and 08"
author: "BA White"
date: "2/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(tidyverse)
library(stringr)
library(readr)

## Challenge 1

## Quote as a vector
quote <- "There is grandeur in this view of life, with its several powers, having been originally breathed by the Creator into a few forms or into one; and that, whilst this planet has gone circling on according to the fixed law of gravity, from so simple a beginning endless forms most beautiful and most wonderful have been, and are being evolved."

## Vector with individual words as elements
split<- str_split(quote, " ")

## Removing puncutation 
gsub("[[:punct:]]","",quote)

## Extraction of every fourth element in a vector
4 <- split[seq(from=1, to=60, by=4)]

print(4)

##Alphabetize 
sort(split, alphabetical = TRUE)


## Challenge 2
## Challenge 3
## Challenge 4

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
