---
title: "MODULES 07 and 08"
author: "BA White"
date: "2/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(tidyverse)
library(stringr)
library(readr)

## Challenge 1

## Quote as a vector
quote <- "There is grandeur in this view of life, with its several powers, having been originally breathed by the Creator into a few forms or into one; and that, whilst this planet has gone circling on according to the fixed law of gravity, from so simple a beginning endless forms most beautiful and most wonderful have been, and are being evolved."

## Vector with individual words as elements
split<- str_split(quote, " ")

## Removing puncutation 
gsub("[[:punct:]]","",quote)

## Extraction of every fourth element in a vector
n<- split[seq(1, length(split), 4)]
print(n)

##Alphabetize 
sort(split, alphabetical = TRUE)

## Challenge 2
## construct a matrix
m1 <- matrix(data = 1:59, nrow = 8, ncol = 10, byrow = FALSE)
m1

## Extract row 5, column 2
m1E <- m1[5,2]
m1E

## Extract row 5 to 7
m1E2<- m1[5:7]
m1E2

## Extract row 3, col 4 to row 6, col 9
m2 <- m1[3:6, 4:9]
m2
class(m2)

## Challenge 3
## Construct an array (5x5 X 4x4)

a <- array(data = 400:1, dim = c(5,5,4,4), descending = TRUE)
a
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]

## Challenge 4

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
